Reading Notes

### 2020-08-06 2pd.tex
dded some notes and commands for ej and cj to comment

\section*{Motivation}
<why do opvs matter>
<the climate is in crisis, energy consumption of fossil fuels strongly increases CO2 output which affects our climate>\cite{Solomon2009a}
<energy demand is increasing and we need a nonpolluting cost-efficient way to provide electricity>
Global energy consumption 17 TW in 2010 to 27 TW in 2040 \cite{Mazzio2015}
Renewable energy is necessary.
Organic photovoltaics (OPVs) are a potential solution.
<image from nrel about solar cells efficiency>\cite{https://www.nrel.gov/pv/cell-efficiency.html}
OPVs are lightweight, low-cost, and flexible--in order to become the best solution they need better efficiency \cite{Mazzioi2015}.
Currently OPV devices are not efficient enough to solve this problem.
In order to make the most efficient opvs we need to find the best blend of compounds and the processing conditions that result in the best structure for those compounds.
<opv performance is intimately linked with structure>
the interfacial area of the acceptor/donor regions \cite{mazzio} the regioregularity of the polymer \cite{Kim2006} and electronic properties (HOMO level) of the compounds \cite{Scharber2006a}
With minor modifcations the number of compounds and the processing conditions can become infinite which makes this an intractable problem for experiment.
Functionalizing a molecule like ITIC can change how it packs in a crystal \cite{Swick2019a}.
By using a simulation pipeline, we can help to streamline the process of determining which opv materials will help to solve the energy crisis
Simulation also helps to give us insight into the atomic interaction which drive self assembly.
A complication of this simulation is that the features which are important to the performance of an opv span multiple length scales.
The electronic properties are important for light absorption, charge transfer \cite{Scharber2006,Hoppe2004,Mazzio2015}
while the bulk morphological properties are important: an exciton needs to be able to find an interface at which to dissociate before it decays through one of its non-radiative processes and one the charges are separated they need to reach an electrode in order to generate current and produce electricity.
<how do we model this system?>

<justification for what I'm doing>
the number of opv compounds to test quickly becomes intractable when we consider that the power conversion efficiency is strongly linked to minor chemical modifications or functionalization, device processing, and the interplay between donor and acceptor\cite{Mazzio2015,Swick2019a}.
There are countless variations of electron donor polymers, fullerene acceptors, and more recently small molecule, non-fullerene acceptors (NFAs) have been recieving attention for their potential to achieve higher efficiencies\cite{dou2013}.
A P3HT:NFA blend was shown to have 11\% PCE, compared to the state-of-the-art 6.4\% in P3HT:PCBM. \cite{Baran2017}
Not only are NFAs found to be more efficient, but they also show to be more stabile in air than polymer:fullerene blends (retaining 70-80\% of the PCE after 1,200 h exposed to air while the fullerene device was no longer operational after 800 h) \cite{Baran2017}.
It is necessary to develop a simple easy to use pipeline to adapt to the constant changing chemistries of current OPV technologies. 
we need a flexible pipeline for coarse grain model generation for these new chemistries

@@

\subsection*{Organic Photovoltaics}
<history>
inorganic PV devices came first and are still most efficient, but they are more costly to produce, use rare elements, other environmental issue--they aren't the best solution for solar energy harvesting. 
first opv was \cite{Tang1986b} used a bilyaer structure
Saricifti and Heeger 1992 \cite{Saricifti1992} used polymer:fullerene mixture.
BHJ with fullerene acceptor reported by Yu in 1995 -still state of the art morphology. \cite{Yu1995}
non fullerene acceptors, like ITIC, are helping to increase PCE \cite{S.Gurney2019}
The planar A-D-A structure may have more efficient exciton splitting, as compared to a fullerene accpetor, at the heterojunction due to strong electronic coupling between the conjugated backbones of the NFA and the polymer \cite{Yi2018}.

@@

<segue from automated creation of forcefields to...>
<mapping operator has to be decided by hand> <is this section too big?>
Part of coarse graining that is not yet automated is choosing a mapping scheme or a mapping operator.
A mapping operator defines which atoms are grouped into a "super atom" represented by one coarse grain site and where in the site is placed relative to the atom group.
Mapping operators are chosen based on desired resolution of the coarse grain system and the information to be extracted.
A straightforward way to define a mapping operator is to group a set number of heavy atoms (non hydrogen) together--this is the method used in the MARTINI force field\cite{Marrink2007}.
In this scheme, four atoms (except rings, which are treated differently) are grouped and the site is classified as polar, non-polar, apolar, or charged depending on the atoms it is composed of.
When parameterizing a new molecule you must pick a mapping and then compare the resulting beads to existing beads--a process which is time consuming and error prone\cite{http://www.cgmartini.nl/index.php/tutorials-general-introduction-gmx5/parametrzining-new-molecule-gmx5}.
The MARTINI force field was first designed for lipids--further parameterization for proteins and nuclei acids have been added<cite--and has shown to be effective in predicting vesicle formation, membrane protein dynamics, etc.
Many mapping schemes are simply based on the user's chemical intuition (e.g., what parts of the molecule shouldn't be allowed to bend?<cite any model where rings are one bead> What groups have the most dominant interactions in this structure <cite dna cg model>).
As the number of atoms in the fine grain structure increases, the number of possible mappings increase drastically.
There have been efforts to create mapping schemes for automating the process of deciding which atoms are grouped in a "super-atom" bead.
One study reduced the number of allowed mappings by only allowing those which do not change the symmetry group, then iterated over a graph of all possible mappings to find the "best" mapping by comparing the difference between the mapped RDF and velocity autocorrelation function \cite{Chakraborty2018a}.
Another mapping scheme uses principle component analysis to choose a mapping scheme for biomolecules that best represents th essential dynamics\cite{Zhang2008}.
Mapping operators can be automated using machine learning: clustering methods combined with graph analysis were shown to predict the "expert" mapping chosen using chemical intuition reliably\cite{li2020}. 
A mapping operator based on the centers of charge was shown to accurately model electrostatic properties\cite{Cao2015a}.

>>>>

\newcommand{\ej}[1]{\textcolor{red}{\textit{#1} -- EJ.}}
\newcommand{\cj}[1]{\textcolor{orange}{\textit{#1} -- CJ.}}
\section*{Motivation}
<why do opvs matter>
<the climate is in crisis, energy consumption of fossil fuels strongly increases CO2 output which affects our climate>\cite{Solomon2009a}
<energy demand is increasing and we need a nonpolluting cost-efficient way to provide electricity>
Global energy consumption 17 TW in 2010 to 27 TW in 2040 \cite{Mazzio2015}
Renewable energy is necessary.
Organic photovoltaics (OPVs) are a potential solution.
<image from nrel about solar cells efficiency>\cite{https://www.nrel.gov/pv/cell-efficiency.html}
OPVs are lightweight, low-cost, and flexible--in order to become the best solution they need better efficiency \cite{Mazzioi2015}.
Currently OPV devices are not efficient enough to solve this problem.
In order to make the most efficient opvs we need to find the best blend of compounds and the processing conditions that result in the best structure for those compounds.
<opv performance is intimately linked with structure>
the interfacial area of the acceptor/donor regions \cite{Mazzio2015} the regioregularity of the polymer \cite{Kim2006} and electronic properties (HOMO level) of the compounds \cite{Scharber2006a}
With minor modifcations the number of compounds and the processing conditions can become infinite which makes this an intractable problem for experiment.
Functionalizing a molecule like ITIC can change how it packs in a crystal \cite{Swick2019a}.
By using a simulation pipeline, we can help to streamline the process of determining which opv materials will help to solve the energy crisis
Simulation also helps to give us insight into the atomic interaction which drive self assembly.
A complication of this simulation is that the features which are important to the performance of an opv span multiple length scales.
The electronic properties are important for light absorption, charge transfer \cite{Scharber2006,Hoppe2004,Mazzio2015}
while the bulk morphological properties are important: an exciton needs to be able to find an interface at which to dissociate before it decays through one of its non-radiative processes and one the charges are separated they need to reach an electrode in order to generate current and produce electricity.
<how do we model this system?>

<justification for what I'm doing>
the number of opv compounds to test quickly becomes intractable when we consider that the power conversion efficiency is strongly linked to minor chemical modifications or functionalization, device processing, and the interplay between donor and acceptor\cite{Mazzio2015,Swick2019a}.
There are countless variations of electron donor polymers, fullerene acceptors, and more recently small molecule, non-fullerene acceptors (NFAs) have been recieving attention for their potential to achieve higher efficiencies\cite{Dou2013}.
A P3HT:NFA blend was shown to have 11\% PCE, compared to the state-of-the-art 6.4\% in P3HT:PCBM. \cite{Baran2017}
Not only are NFAs found to be more efficient, but they also show to be more stabile in air than polymer:fullerene blends (retaining 70-80\% of the PCE after 1,200 h exposed to air while the fullerene device was no longer operational after 800 h) \cite{Baran2017}.
It is necessary to develop a simple easy to use pipeline to adapt to the constant changing chemistries of current OPV technologies. 
we need a flexible pipeline for coarse grain model generation for these new chemistries

@@

\subsection*{Organic Photovoltaics}
<history>
<what is PCE>
inorganic PV devices came first and are still most efficient, but they are more costly to produce, use rare elements, other environmental issue--they aren't the best solution for solar energy harvesting. 
first opv was \cite{Tang1986b} used a bilyaer structure copper phthalocyanine and a perylene derivitive (PCE 0.95\%)
Saricifti and Heeger 1992 \cite{Saricifti1992} were the first to report using fullerene as an electron acceptor in a fullerene:polymer mixture.
Yu in 1995 described the first BHJ, an interpenetrating network of donor and acceptor that maximizes the interfacial area, which is still the state of the art morphology. \cite{Yu1995}
Non-fullerene acceptors, like ITIC, are helping to increase PCE \cite{S.Gurney2019}
The planar A-D-A structure may have more efficient exciton splitting, as compared to a fullerene accpetor, at the heterojunction due to strong electronic coupling between the conjugated backbones of the NFA and the polymer \cite{Yi2018}.

@@

<segue from automated creation of forcefields to...>
<mapping operator has to be decided by hand> <is this section too big?>
Part of coarse graining that is not yet automated is choosing a mapping scheme or a mapping operator.
A mapping operator defines which atoms are grouped into a "super atom" represented by one coarse grain site and where in the site is placed relative to the atom group.
Mapping operators are chosen based on desired resolution of the coarse grain system and the information to be extracted.
A straightforward way to define a mapping operator is to group a set number of heavy atoms (non hydrogen) together--this is the method used in the MARTINI force field\cite{Marrink2007}.
In this scheme, four atoms (except rings, which are treated differently) are grouped and the site is classified as polar, non-polar, apolar, or charged depending on the atoms it is composed of.
When parameterizing a new molecule you must pick a mapping and then compare the resulting beads to existing beads--a process which is time consuming and error prone\cite{http://www.cgmartini.nl/index.php/tutorials-general-introduction-gmx5/parametrzining-new-molecule-gmx5}.
The MARTINI force field was first designed for lipids--further parameterization for proteins and nuclei acids have been added<cite--and has shown to be effective in predicting vesicle formation, membrane protein dynamics, etc.
Many mapping schemes are simply based on the user's chemical intuition (e.g., what parts of the molecule shouldn't be allowed to bend?<cite any model where rings are one bead> What groups have the most dominant interactions in this structure <cite dna cg model>).
As the number of atoms in the fine grain structure increases, the number of possible mappings increase drastically.
There have been efforts to create mapping schemes for automating the process of deciding which atoms are grouped in a "super-atom" bead.
One study reduced the number of allowed mappings by only allowing those which do not change the symmetry group, then iterated over a graph of all possible mappings to find the "best" mapping by comparing the difference between the mapped RDF and velocity autocorrelation function \cite{Chakraborty2018a}.
Another mapping scheme uses principle component analysis to choose a mapping scheme for biomolecules that best represents th essential dynamics\cite{Zhang2008}.
Mapping operators can be automated using machine learning: clustering methods combined with graph analysis were shown to predict the "expert" mapping chosen using chemical intuition reliably\cite{Li2020}. 
A mapping operator based on the centers of charge was shown to accurately model electrostatic properties\cite{Cao2015a}.
